# (PART) 1st Ed. Exercises {-}


# Solutions Formatting {#intro}


### Option 1
(nice output, indentation in source makes it harder to read ; current)


1.  __<span style="color:red">Q</span>__: The following code accesses the mean function in multiple different ways. Do they all point to the same underlying function object? Verify with `lobstr::obj_addr()`.
    
    ```{r, eval = FALSE}
    mean
    base::mean
    get("mean")
    evalq(mean)
    match.fun("mean")
    ```
    
    __<span style="color:green">A</span>__: Yes, they point to the same object. To confirm that, we look at the address of the underlying function object. Since `lobstr::obj_addr()` currently returns an error, we use `pryr::address()` to inspect the addresses:


### Option 2
(clean source, no html markup)

***Question 1** The following code accesses the mean function in multiple different ways. Do they all point to the same underlying function object? Verify with `lobstr::obj_addr()`.*
    
```{r, eval = FALSE}
mean
base::mean
get("mean")
evalq(mean)
match.fun("mean")
```

**Answer:** Yes, they point to the same object. To confirm that, we look at the address of the underlying function object. Since `lobstr::obj_addr()` currently returns an error, we use `pryr::address()` to inspect the addresses:


### Option 3
(5th level header provides most structure in rmd source)

###### Question 1: The following code accesses the mean function in multiple different ways. Do they all point to the same underlying function object? Verify with `lobstr::obj_addr()`. {.unnumbered}
    
```{r, eval = FALSE}
mean
base::mean
get("mean")
evalq(mean)
match.fun("mean")
```

Yes, they point to the same object. To confirm that, we look at the address of the underlying function object. Since `lobstr::obj_addr()` currently returns an error, we use `pryr::address()` to inspect the addresses:

### Option 4
(R4DS-Solutions-Style)

### Exercise <span class="exercise-number">1.1.1</span> {.unnumbered .exercise}

<div class="question">
> The following code accesses the mean function in multiple different ways. Do they all point to the same underlying function object? Verify with `lobstr::obj_addr()`.

```{r, eval = FALSE}
mean
base::mean
get("mean")
evalq(mean)
match.fun("mean")
```
</div>

<div class="answer">
Yes, they point to the same object. To confirm that, we look at the address of the underlying function object. Since `lobstr::obj_addr()` currently returns an error, we use `pryr::address()` to inspect the addresses:
</div>